Comparing R packages for calculation of persistent homology

### 2020-03-19 tdabench-paper/tdabench.Rmd
math mode for vars

Figure \ref{fig:fin} shows that at high point cloud sizes, GUDHI’s alpha complex outperforms Ripser. 
Theoretically, alpha complexes gain polynomial complexity as the number of points increases whereas Vietoris-Rips complexes gain exponentially \citep{roadmap}.
Specifically, alpha complexes are $O(n^{d/2})$ and Vietoris-Rips complexes are $O(2^n)$ where n is the number of points on a point cloud and d is the dimensions on the point cloud. 
For the conditions in our paper, Vietoris-Rips and alpha complexes both performed better than their theoritical maximums. 
Vietoris-Rips complex calculations consistently had a polynomial growth for both runtime and boundary matrix size while alpha complexes had linear growth.

>>>>

Figure \ref{fig:fin} shows that at high point cloud sizes, GUDHI’s alpha complex outperforms Ripser. 
Theoretically, alpha complexes gain polynomial complexity as the number of points increases whereas Vietoris-Rips complexes gain exponentially \citep{roadmap}.
Specifically, alpha complexes are $O(n^{d/2})$ and Vietoris-Rips complexes are $O(2^n)$ where $n$ is the number of points on a point cloud and $d$ is the dimensions on the point cloud. 
For the conditions in our paper, Vietoris-Rips and alpha complexes both performed better than their theoritical maximums. 
Vietoris-Rips complex calculations consistently had a polynomial growth for both runtime and boundary matrix size while alpha complexes had linear growth.
